The Cost of Undisturbed Landscapes

### 2020-04-30 projects/asparagus/doc/paper_clean.tex
updates medea_asparagus.gms to restrict technology additions

%    Further uncertainty surrounds
%    •	Storage prices
%    •	Weather / full-load hours
%    •	LOOK AT WHAT HAPPENS WHEN GERMANY BUILDS MORE PV THAN ANTICIPATED (particularly in the low pv-cost scenario)

>>>>

%    Further uncertainty surrounds
%    •	Storage prices
%    •	Weather / full-load hours
%    •	LOOK AT WHAT HAPPENS WHEN GERMANY BUILDS MORE PV THAN ANTICIPATED (particularly in the low pv-cost scenario)
    Effect of \COO prices on opportunity cost of wind power:
    - lower \COO price means less 'voluntary' RET installed
    - more PV means more ancillary capacities installed (?)
    - more PV means more fuel used in dispatchable plant
    - more PV means more curtailment (?)
    - more PV means lower exports -- large dependency on \COO price. At price of 60-120, exports fall as less wind.
    For low \COO price exports increase as less wind. -->> Need to look at capacities in Germany!
    - more PV means
    * PV capacity at full wind substitution is (almost) invariant to \COO price and comes in at 24.11-24.26 GW
    * wind on capacity is sensitive to \COO price. At 120 \EUR \COO, 17.07 GW wind on added, at 0 \EUR \COO10.43 GW added
    * austria builds coal plants -- this should be impossible! --> correct in re-run
    * austria builds oil instead of nat gas plants. --> check and potentially correct cost versus HAt gas
    * absolutely no heatpump added. why?

    + Germany add lignite and coal. With rising \COO price more coal is added. (!)
    + Germany adds oil. At lower \COO price more oil, less ng added
    + No bio added in Germany (proly restriction)
    + No heatpumps added --> Why???
    + Germany adds PV and wind only with \COO price at 120

    Need to re-run model with restricted additions
